---
title: "Functions"
author: "Andreas Muenchow"
date: "10/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Assemble functions into an R-file, then call them here as 'source'
```{r}
library(roxygen2)
source("conversions.R")
```
# Functions
DRY - Do not repeat yourself.
```{r}
t_f <- c(212,32,0)
```
Write function
`{r}

#' Convert from Fahrenheit to Celsius

#'

#' A more detailed explanation of how function works

#'

#' @param fahr represents numeric input in Fahrenheit

#' @return temperature in Celsius

#' @export

#' @expample fahr_to_celsius(212)

#'
fahr_to_celsius <- function(fahr) {
#  stopifnot(!is.numeric(fahr))
  celsius <- (fahr-32)*5/9
  return(celsius)
}
`
```{r}
celsius1 <- fahr_to_celsius(t_f[1])
celsius1 <- fahr_to_celsius(t_f)
celsius1
```
Inverse
```{r}
#' A more detailed explanation of how function works
#'
#' @param celsius represents numeric input in Fahrenheit
#' @return temperature in Fahrenheit
#' @export
#' @expample fahr_to_celsius(0)
#'
celsius_to_fahr <- function(celsius) {
#  stopifnot(!is.numeric(fahr))
  fahr <- celsius*9/5+32
  return(fahr)
}
  fahr <- celsius_to_fahr(celsius1)
  fahr
```