---
title: "Tidy00"
author: "Andreas Muenchow"
date: "10/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##First exercise of Data Cleaning
``` {r package_load}
library(dplyr)
library(tidyr)
#library(tidyverse)
```

To access 'filter' from 'stats' package
'stats::filter(parameter_list_here_when_run_in_code)'
stringsAsFactors assigns numerical value to a text string found within the csv file, "FALSE" turns this off

# Read in and clean Data

```{r}
catch_original <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/df35b.302.1",method = "libcurl"),stringsAsFactors = FALSE)
head (catch_original)
```

# Tidy
Pipes are defined as '%<% ... everything is backward from Unix in terms of input > output

Select columns we want 'select()' the piping operator always at the end of a line in R
``` {r}
catch_data <- catch_original %>%
#  select(Region,Year,Chinook)
select(-All,-notesRegCode)
summary(catch_data)

```
Change vlaues for chinook
```{r}
catch_clean <- catch_data %>%
mutate(Chinook = as.numeric(Chinook))
head(catch_clean,2)
```
Investigate the NaN with 'which' and 'is.na()'
```{r}
i <- which(is.na(catch_clean$Chinook))
head(i)
catch_original[i,]
```
use 'mutate' to change I to 1
```{r}
catch_clean <- catch_data %>%
 mutate(Chinook = ifelse(Chinook == "I" | Chinook == "l", 1,Chinook)) %>%
#  mutate(Chinook = ifelse(Chinook %in% c("I","l"), 1,Chinook)) %>%
mutate(Chinook = as.numeric(Chinook))
head(catch_clean,2)
```
# Move wide to tall format 'pivot_longer()' where the -c is an exclionary list
``` {r}
catch_long <- catch_clean %>%
  pivot_longer(cols = -c(Region,Year),
               names_to = "species",
               values_to = "catch")
head(catch_long)
```
```{r}
catch_wide <- catch_long %>%
  pivot_wider(names_from = species,
              values_from = catch)
head(catch_wide,2)
```
Rename header and units
```{r}
catch_long <- catch_long %>%
  rename(catch_thousands = catch) %>%
  mutate(catch = catch_thousands * 1000) %>%
  select(-catch_thousands)
head(catch_long,2)
```
# Summarize

Calculate mean catch by region and species
```{r}
mean_region <- catch_long %>%
  group_by(Region, species) %>%
  summarise(mean_catch = mean(catch),
            n_obs=n())
mean_region
```
Example-2 mean sockeye catch by region
```{r}
mean_sockeye <- catch_long %>%
  filter(species == "Sockeye") %>%
  group_by(Region) %>%
  summarize(mean_catch=mean(catch))
mean_sockeye
```
Example-3
```{r}
annual_catch = catch_long %>%
  group_by(Year) %>%
  summarize(total_catch = sum(catch)) %>%
  arrange(desc(total_catch))

annual_catch
```
# Working against my will with VERY messy and disorganized data
```{r}
region_defs <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/df35b.303.1",
                            method = "libcurl"),
                        stringsAsFactors = FALSE) %>%
  select(code,mgmtArea)
head(region_defs)
```
```{r}
catch_joined <- left_join(catch_long, region_defs, by=c("Region" = "code"))
head(catch_joined)
```
```{r}
region_defs <- region_defs %>%
  rename(Region = code)
catch_joined <- left_join(catch_long, region_defs, by = "Region")
head(catch_joined)
```
# New Tools
Toy data frame
```{r}
dates_df <- data.frame(date = c("5/24/1930",
                                "5/25/1930",
                                "5/26/1930",
                                "5/27/1930",
                                "5/28/1930"),
                       stringsAsFactors = FALSE)

dates_df %>% 
  separate(date, into = c("month", "day", "year"), sep = "/", remove=FALSE) %>%
unite(date_2,year,month,day,sep="-")
```